Asimilación de distintas observaciones

### 2022-05-03 analysis/chapters/experimento_20181122.Rmd
tidying folders.

```{r dbz-ens}
files <- Sys.glob(paste0(derived_data, "dbz/maxdbz_ana_E[4-7]_0*_20181122100000.nc"))

@@

dbz %>% 
  .[, .(max_dbz = mean(max_dbz, na.rm = TRUE)), by = .(cumulus, exp, date, lon, lat, x, y)] %>% 
  # .[date %in% unique(date)[1:2]] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level)), 
                    proj = norargentina_lambert,
                    breaks = values) +
  scale_fill_manual(values = colours, 
                    drop = FALSE, guide = guide_colorsteps(barwidth = 0.8, 
                                                           barheight = 30)) +
  geom_mapa() +
  ggh4x::facet_nested(date + cumulus ~ exp, 
                      labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                  E6 = "SATWND", E7 = "RAD"))) +
  labs(fill = NULL) +
  theme_minimal() +
  theme(#legend.position = "bottom",
    legend.box.spacing = margin(0, 0, 0, 0),
    panel.ontop = TRUE,
    panel.grid = element_line(linetype = 3))

# rm(dbz)
```
#### FSS for the analysis

>>>>

```{r dbz-ens}
files <- Sys.glob(paste0(derived_data, "dbz/maxdbz_ana_E[5,6,8]_0*_20181122130000.nc"))

@@

colours <- c("#3D4170", "#3D4E7C", "#3B5B84", "#3A6695", "#3672A4", "#3188BD", 
             "#2F89B9", "#2896C7", "#24A4CF", "#2AB1D6", "#53F336", "#4BE231", 
             "#44D12F", "#3FC12B", "#3AAF25", "#32A11F", "#2C881E", "#227216", 
             "#EEEF39", "#DEE539", "#D7DA35", "#CED130", "#C4C52B", "#CBAE1F", 
             "#D59716", "#DB8116", "#EC0A2E", "#CB001A", "#C20013", "#B10009", 
             "#990000", "#C3005D", "#D600A2", "#E901E9", "#CC00CC", "#B100B5", 
             "#9800A0", "#FEFFFF", "#DFF5EC", "#C5F1E0", "#B7ECD8", "#A6ECCF", 
             "#95E3C5", "#85E0BD")

dbz %>% 
  .[, .(max_dbz = mean(max_dbz, na.rm = TRUE)), by = .(cumulus, exp, date, lon, lat, x, y)] %>% 
  # .[date %in% unique(date)[1:2]] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level)), 
                    proj = norargentina_lambert,
                    breaks = values) +
  scale_fill_manual(values = colours, 
                    labels = function(x) JumpBy(x, 3, fill = ""),
                    drop = FALSE, 
                    guide = guide_colorsteps(barwidth = 25,
                                             barheight = 0.4, 
                                             title.position = "left", 
                                             title.vjust = 1,
                                             frame.colour = "black")) +
  geom_mapa() +
  ggh4x::facet_nested(date + cumulus ~ exp, 
                      labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                  E6 = "SATWND", E8 = "RAD"))) +
  labs(fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
    legend.box.spacing = margin(0, 0, 0, 0),
    panel.ontop = TRUE,
    panel.grid = element_line(linetype = 3))

# rm(dbz)

dbz %>% 
  .[, .(max_dbz = mean(max_dbz, na.rm = TRUE)), by = .(exp, date, lon, lat, x, y)] %>% 
  # .[date %in% unique(date)[1:2]] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level)), 
                    proj = norargentina_lambert,
                    breaks = values) +
  scale_fill_manual(values = colours, 
                    labels = function(x) JumpBy(x, 3, fill = ""),
                    drop = FALSE, 
                    guide = guide_colorsteps(barwidth = 25,
                                             barheight = 0.4, 
                                             title.position = "left", 
                                             title.vjust = 1,
                                             frame.colour = "black")) +
  geom_mapa() +
  # ggh4x::facet_nested(date + cumulus ~ exp, 
  #                     labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
  #                                                 E6 = "SATWND", E8 = "RAD"))) +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                  E6 = "SATWND", E8 = "RAD"))) +
  labs(fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
    legend.box.spacing = margin(0, 0, 0, 0),
    panel.ontop = TRUE,
    panel.grid = element_line(linetype = 3))
```
#### FSS for the analysis
